\ldots

### 2016-02-04 paper.tex
A figure listing all parameters

Another issue with PMI is its bias towards rare events \cite{TACL570} one way of solving this issue is to weight PMI value by the co-occurrence frequency \cite{Evert05}:
%
\begin{equation}
  \label{eq:lmi}
  \operatorname{LMI}(x, y) = n\operatorname{PMI}(x, y)
\end{equation}
%
where $n$ is the number of times $x$ was seen together with $y$. For clarity, we refer to $n$ weighted PMIs as \NPMI/, \NPPMI/ \NCPMI/ and \NPCPMI/. When frequency component is set to 1, it does not have an effect giving rise to explicit quantification labels: \PMI/, \PPMI/, \CPMI/ and \PCPMI/.

@@

As context words we select 1000, 2000, 3000, 5000, 10000, 20000, 30000, 40000 and 50000 most frequent nouns, verbs, adjectives and adverbs. All context words are part of speech tagged, but we do not make difference between refined word types, for example, we do not distinguish between transitive and ditransitive verbs.

@@

>>>>

Another issue with PMI is its bias towards rare events \cite{TACL570} one way of solving this issue is to weight PMI value by the co-occurrence frequency \cite{Evert05}:
%
\begin{equation}
  \label{eq:lmi}
  \operatorname{LMI}(x, y) = n(x, y)\operatorname{PMI}(x, y)
\end{equation}
%
where $n(x, y)$ is the number of times $x$ was seen together with $y$. For clarity, we refer to $n$ weighted PMIs as \NPMI/, \NPPMI/ \NCPMI/ and \NPCPMI/. When frequency component is set to 1, it does not have an effect giving rise to explicit quantification labels: \PMI/, \PPMI/, \CPMI/ and \PCPMI/.

@@

As context words we select 1000, 2000, 3000, 5000, 10000, 20000, 30000, 40000 and 50000 most frequent lemmatised nouns, verbs, adjectives and adverbs. All context words are part of speech tagged, but we do not make difference between refined word types, for example, we do not distinguish between transitive and ditransitive verbs.

@@

\begin{figure*}[th]
  \centering
  \begin{tabular}{llr}
    \toprule
    % \multicolumn{2}{c}{Item} \\
    % \cmidrule(r){1-2}
    Parameter & Values \\
    \midrule
    \texttt{discr} & PMI, CPMI, PosPMI, PCPMI \\
    \texttt{neg} & 0.5, 0.7, 1, 1.4, 2, 5 \\
    \texttt{freq} & $1$, $n$, $\log n$ \\
    \texttt{cds} & \textit{nan}, 1, 0.75 \\
    Dimensionality & 1K, 2K, 3K, 5K, 10K, 20K, 30K, 40K, 50K \\
    Similarity & cosine, correlation \\
    \multirow{2}{*}{Compositional operator}
              & add, mult, kron, relational,
                copy-object, copy-subject, \\
              & frobenious-add, frobenious-mult,
                frobenious-outer
    \\
    Corpus & concatenation of ukWac and Wackypedia \\
    Window size & 5 \\
    \bottomrule
  \end{tabular}
  \caption{\textbf{Parameters and their values.}}
\end{figure*}
